---
title: "3_prep_data_for_analysis"
format: html
editor: visual
---

## Continue environment setup

## Load packages

Load packages for use in subsequent scripts:

```{r}
library(data.table)
library(plyr)
library(dplyr)
library(magrittr)
library(lubridate)
library(readr)
library(survival)
library(Epi)
library(emmeans)
library(ggplot2)
library(ckbplotr)
```

## Set-up useful functions

```{r}
source("useful_functions/rounding_functions.R")
source("useful_functions/cut_by_quantile.R")
```

## Create necessary folders

```{r}
dir.create("data")
dir.create("outputs")
```

## Load data

```{r}
dat_orig <- fread("/path/to/ukb/data/", data.table = FALSE) 
dat_hes <- fread("/path/to/ukb/hes/data/", data.table = FALSE)
dat_death <- fread("/path/to/ukb/death/data/", data.table = FALSE)
dat_death_cause <- fread("path/to/ukb/death/cause/data", data.table = FALSE)
dat_acc <- fread("/path/to/ukb/stepcount/data", data.table = FALSE)
```

Manipulate data:

```{r}
cols_dat <-
  c(
    "eid",
    "sex",
    "year_birth",
    "month_birth",
    "ethnicity_raw",
    "ukb_assess_cent",
    "date_baseline",
    "date_lost_followup",
    "tdi_raw",
    "qualif_raw",
    "alcohol_raw",
    "smoking_raw",
    "Fresh fruit intake | Instance 0", 
    "Processed meat intake | Instance 0", 
    "Oily fish intake | Instance 0",
    "Salt added to food | Instance 0", 
    "Overall health rating | Instance 0",
    "Usual walking pace | Instance 0",
    "BMI_raw",
    "date_end_accel",
    "quality_good_wear_time",
    "Wear duration overall",
    "quality_good_calibration",
    "clips_before_cal",
    "clips_after_cal",
    "total_reads",
    "overall_activity"
  )
cols_dat_hes <- c(
  "eid",
  "dnx_hesin_id",
  "dnx_hesin_diag_id",
  "dateepiimp",
  "ins_index",
  "arr_index",
  "level",
  "diag_icd9",
  "diag_icd9_nb",
  "diag_icd10",
  "diag_icd10_nb"
)
dat <- dat_orig[, cols_dat]
dat_hes <- dat_hes[, cols_dat_hes]
```

We inspect the data structure to check all columns are the types we expect:

```{r}
for (data in list(dat, dat_hes, dat_death, dat_death_cause)){
    str(data, vec.len = 0) # vec.len = 0 avoids accidentally printing data
}
```

We also do some simple formatting of date columns:

```{r}
# Tabular participant data
dat$date_lost_followup <- as.Date(dat$date_lost_followup, format = "%Y-%m-%d")
dat$date_end_accel <- as.Date(dat$date_end_accel, format = "%Y-%m-%d")
dat$date_baseline <- as.Date(dat$date_baseline, format = "%Y-%m-%d") 

# Hospital data
dat_hes$date_hes <- as.Date(dat_hes$dateepiimp, format = "%Y-%m-%d")

# Death data
dat_death$date_death <-
  as.Date(dat_death$date_of_death, format = "%Y-%m-%d")
# A very small number of participants have duplicate records in death data (e.g. perhaps from a second death certificate after post-mortem)
# In this dataset we keep just one record per participant: they should have the same date, and we will use the death_cause dataset for any 
# other records related to death. It also only affects a very small number of participants.
dat_death <-
  dat_death[dat_death$ins_index == 0, ]
```

## Hospital record data

We will use the hospital record data to identify prior disease (cardiovascular disease, cancer).

We only use level 1 codes associated with the admission (primary diagnoses) to avoid being too sensitive to incidental codes (e.g. hypertension while in hospital with something unrelated)

Processing prior primary CVD:

```{r}
# The lists of ICD codes we will consider------------------
icd10_codes <- "I" # All I codes = all cardiovascular codes

# Restrict the hospital data frame to occurrences of these codes with level == 1-------------------------------------------------
dat_hes_rel <-
  dat_hes[grepl(icd10_codes, dat_hes$diag_icd10) &
          (dat_hes$level == 1),
          c("eid", "date_hes", "diag_icd10")]

# Find first occurrence----------------------------------------
dat_hes_first_cvd <-
  aggregate(dat_hes_rel$date_hes, list(dat_hes_rel$eid), min)
colnames(dat_hes_first_cvd) <- c("eid", "date_hes_first_cvd")

# Merge into main data frame-----------------------------------
dat <- merge(
  dat,
  dat_hes_first_cvd,
  by = "eid",
  all.x = TRUE,
  suffixes = c("", "dup") # This just means that if we accidentally run it twice we won't rename the columns (although running it more than twice still gets weird)
)
```

We now add indicator variables for primary CVD and whether it was prevalent (before accelerometer wear):

```{r}
# Add indicators of any primary cvd and prevalent primary CVD
dat$ind_hes_cvd <- !is.na(dat$date_hes_first_cvd)
dat$ind_prev_hes_cvd <- dat$ind_hes_cvd & (dat$date_hes_first_cvd <= dat$date_end_accel)
```

Processing prior primary cancer:

```{r}
# The lists of ICD codes we will consider------------------
icd10_codes <- "C"

# Restrict the hospital data frame to occurrences of these codes with level == 1-------------------------------------------------
dat_hes_rel <-
  dat_hes[grepl(icd10_codes, dat_hes$diag_icd10) &
            (dat_hes$level == 1),
          c("eid", "date_hes", "diag_icd10")]

# Find first occurrence----------------------------------------
dat_hes_first_can <-
  aggregate(dat_hes_rel$date_hes, list(dat_hes_rel$eid), min)
colnames(dat_hes_first_can) <- c("eid", "date_hes_first_can")

# Merge into main data frame-----------------------------------
dat <- merge(
  dat,
  dat_hes_first_can,
  by = "eid",
  all.x = TRUE,
  suffixes = c("", "dup") # This just means that if we accidentally run it twice we won't rename the columns
)
```

We now add indicator variables for primary cancer and whether it was prevalent (before accelerometer wear):

```{r}
# Add indicators of any primary cancer and prevalent primary cancer
dat$ind_hes_can <- !is.na(dat$date_hes_first_can)
dat$ind_prev_hes_can <- dat$ind_hes_can & (dat$date_hes_first_can <= dat$date_end_accel)
```

## Variables

### Age

Age at accelerometer wear:

```{r}
# Add date of birth
dat$approx_dob <-
  as.Date(paste(dat$year_birth, dat$month_birth, "15", sep = "-"),
          "%Y-%B-%d") # UK Biobank doesn't contain day of birth as it would be unnecessary identifying information, so we roughly impute it as the 15th of the birth month.

# Add age at entry in days
dat$age_entry_days <-
  difftime(dat$date_end_accel,
           dat$approx_dob,
           units = "days")

# Convert to age at entry in years
dat$age_entry_years <- as.double(dat$age_entry_days)/365.25
```

### Sex

Male, female

### Age

40-44 \[note this is really 43-44\]; 45-49; 75-79

```{r}
# Add age groups
dat$age_gp <-
  cut(
    dat$age_entry_years,
    breaks = c(40, 45, 50, 55, 60, 65, 70, 75, 80),
    right = FALSE
  )
```

### Ethnicity

White, non-white

```{r}
# Ethnicity
dat$ethnicity <-
  plyr::revalue(
    dat$ethnicity_raw,
    c(
      "British" = "White",
      "Any other white background" = "White",
      "Irish" = "White",
      "White and Asian" = "Nonwhite",
      "Caribbean" = "Nonwhite",
      "Chinese"   = "Nonwhite",
      "Pakistani"  = "Nonwhite",
      "White and Black African" = "Nonwhite",
      "Other ethnic group"  = "Nonwhite",
      "Any other mixed background" = "Nonwhite",
      "African"    = "Nonwhite",
      "White and Black Caribbean" = "Nonwhite",
      "Prefer not to answer" = NA,
      "Indian"  = "Nonwhite",
      "White" = "White",
      "Do not know" = NA,
      "Any other Black background" = "Nonwhite",
      "Any other Asian background"  = "Nonwhite",
      "Bangladeshi"  = "Nonwhite",
      "Mixed"  = "Nonwhite",
      "Asian or Asian British"  = "Nonwhite",
      "Black or Black British"  = "Nonwhite"
    )
  )
```

### BMI

```{r}
# BMI
dat$BMI <- dat$BMI_raw
```

### Education

School leaver, further education, higher education

```{r}
dat$qualif <- NA
dat$qualif[grepl("degree", dat$qualif_raw)] <-
  "Higher education"
dat$qualif[is.na(dat$qualif) & grepl("A level|NVQ|professional", dat$qualif_raw)] <- "Further education"
dat$qualif[is.na(dat$qualif) & grepl("GCSEs|CSEs|None", dat$qualif_raw)] <- "School leaver"
```

### Smoking status

Never, Former, Current

```{r}
# Smoking
dat$smoking <-
  plyr::revalue(dat$smoking_raw, replace = c("Prefer not to answer" = NA))
```

### Alcohol consumption

```{r}
# Alcohol
dat$alcohol <-
  plyr::revalue(
    dat$alcohol_raw,
    replace = c(
      "Prefer not to answer" = NA,
      "Three or four times a week" = "3+ times/week",
      "Special occasions only" = "<3 times/week",
      "One to three times a month" = "<3 times/week",
      "Daily or almost daily" = "3+ times/week",
      "Once or twice a week" = "<3 times/week"
    )
  )
```

### TDI

By quarter in population

### Fresh fruit

```{r}
dat$fresh_fruit_numeric <-
  plyr::revalue(
    dat$`Fresh fruit intake | Instance 0`,
    replace = c(
      "Less than one" = "0.5",
      "Do not know" = NA,
      "Prefer not to answer" = NA
    )
  )
dat$fresh_fruit <-
  cut(as.double(dat$fresh_fruit_numeric),
      c(0, 1.999, 2.999, 3.999, 100000),
      right = FALSE)
```

### Processed meat

```{r}
dat$processed_meat <-
  plyr::revalue(
    dat$`Processed meat intake | Instance 0`,
    replace = c(
      "Do not know" = NA,
      "Prefer not to answer" = NA,
      "Less than once a week" = "Less than twice a week",
      "Once a week" = "Less than twice a week",
      "5-6 times a week" = "5 or more times a week",
      "Once or more daily" = "5 or more times a week"
    )
  )
```

### Oily fish

```{r}
dat$oily_fish <- plyr::revalue(
  dat$`Oily fish intake | Instance 0`,
  replace = c(
    "Do not know" = NA,
    "Prefer not to answer" = NA,
    "Less than once a week" = "Less than twice a week",
    "Once a week" = "Less than twice a week",
    "5-6 times a week" = "5 or more times a week",
    "Once or more daily" = "5 or more times a week"
  )
) 
```

### Salt added to food

```{r}
dat$added_salt <-
  plyr::revalue(
    dat$`Salt added to food | Instance 0`,
    replace = c("Do not know" = NA, "Prefer not to answer" = NA)
  )
```

### Self reported usual walking pace

Slow, Steady, Brisk

```{r}
dat$sr_usual_walking_pace <-
  plyr::revalue(dat$`Usual walking pace | Instance 0`, replace = c("Prefer not to answer" = "Missing"))
dat$sr_usual_walking_pace[dat$sr_usual_walking_pace == ""| is.na(dat$sr_usual_walking_pace)] <- "Missing"
```

### Self-Reported overall health

Excellent, good, fair, poor

```{r}
dat$sr_overall_health <-
  plyr::revalue(
    dat$`Overall health rating | Instance 0`,
    replace = c(
      "Prefer not to answer" = "Missing",
      "Do not know" = "Missing",
      "Excellent" = "Excellent self-rated overall health",
      "Good" = "Good self-rated overall health",
      "Fair" = "Fair self-rated overall health",
      "Poor" = "Poor self-rated overall health"
    )
  )
dat$sr_overall_health[dat$sr_overall_health == "" |
                        is.na(dat$sr_overall_health)] <- "Missing"
```

### Wear season

Spring, Summer, Autumn, Winter

```{r}
dat$month_wear <- month(dat$date_end_accel)
dat$season_wear <- plyr::mapvalues(dat$month_wear,
                                   c(12, 1:11),
                                   c(
                                     rep("Winter", 3),
                                     rep("Spring", 3),
                                     rep("Summer", 3),
                                     rep("Autumn", 3)
                                   ))
table(dat$month_wear, dat$season_wear) # showing Dec-Feb assigned to winter (based on end time of accelerometer wear) and so on
```

### Charlson Comorbidity Index

Definition based on: https://digital.nhs.uk/data-and-information/publications/statistical/shmi/2023-02

```{r}
# SUBSET DATA TO THE 5Y PRIOR TO ACC WEAR ================================================================
dat_hes_w_acc <- merge(dat_hes, dat[, c("eid", "date_end_accel")], all.x = TRUE)
dat_hes_w_acc$time_rel_to_acc <- difftime(dat_hes_w_acc$date_hes, dat_hes_w_acc$date_end_accel, units = "days")
dat_hes_5y_lookback <- dat_hes_w_acc[(dat_hes_w_acc$time_rel_to_acc < 0) & (dat_hes_w_acc$time_rel_to_acc > -365.25*5), ]

# SET UP LIST WITH CHARLSON SCORE INFO ===================================================================
source("useful_functions/load_charlson_codelist.R") # Look at this folder to see the codelist

# CHARLSON COMORBIDITY INDEX CALCULATION =====================================================================
for (disease in names(charlson_codelist)){
  # Prep
  details <- charlson_codelist[[disease]]
  string <- details[[1]]
  weight <- details[[2]]

  # Restrict to relevant ids
  dat_hes_5y_lookback_current_code_ids <- unique(dat_hes_5y_lookback$eid[grepl(string, dat_hes_5y_lookback$diag_icd10)])
  
  # Record
  dat[, paste0(disease, "_charlson")] <- ifelse(dat$eid %in% dat_hes_5y_lookback_current_code_ids, weight, 0)

  # Spit out progress info
  print(disease)
  print(string)
  print(table(dat[, paste0(disease, "_charlson") ]))
  
  # Tidy
  rm(string, weight, details)
}

# Additional rules: 
# Metastatic cancer means ignore cancer code
dat$cancer_charlson[dat$metastatic_cancer_charlson > 0 ] <- 0

# Total score
dat$cci <- apply(dat[, paste0(names(charlson_codelist), "_charlson")] , 1, sum)

# Truncate scores on [0-50]
dat$cci[dat$cci < 0] <- 0 
dat$cci[dat$cci > 50] <- 50
```

## Add various chronic disease indicators

```{r}
source("useful_functions/load_disease_codelist.R")
dat_hes_pre_acc <- dat_hes_w_acc[dat_hes_w_acc$time_rel_to_acc < 0, ]

for (disease in names(disease_codelist)){
  # Extract lists------------------------------------
  icd10_current <- disease_codelist[[disease]][[1]]
  icd9_current <- disease_codelist[[disease]][[2]]
  
  # Filter dataset-----------------------------------
  dat_current_disease_pre_acc <- dat_hes_pre_acc %>% dplyr::filter(diag_icd10 %in% icd10_current | diag_icd9 %in% icd9_current) # could change this to consistent syntax with rest but doesn't seem worth it! 
  
  # Add indicator to frame-----------------------------
  dat[, paste0("prev_hes_", disease)] <- ifelse(dat$eid %in% dat_current_disease_pre_acc$eid, disease, paste0("No_", disease))
  
  # Tidy up-------------------------------------------
  rm(icd10_current, icd9_current, dat_current_disease_pre_acc)
}
```

## Add outcome

-   Death: indicator for death during study period
-   Indicator for that death being CVD

Merge in death data:

```{r}
dat$ind_death_record <- dat$eid %in% dat_death$eid
dat <-
  merge(
    dat,
    dat_death[, c("eid", "date_death")],
    by = "eid",
    all.x = TRUE,
    suffixes = c("", "dup") # This makes it safe if we accidentally run it twice - we won't rename the columns
  )
```

Set up censoring dates:

```{r}
ind_wales <-
  dat$ukb_assess_cent %in% c("Cardiff", "Wrexham", "Swansea")
ind_scotland <- 
  dat$ukb_assess_cent %in% c("Edinburgh", "Glasgow")

dat$date_cens <- "2021-09-30"
dat$date_cens[ind_scotland] <- "2021-10-31"
dat$date_cens <- as.Date(dat$date_cens)
```

\[Note: if there is a new data release you can update these. But beware to:

-   update the outcomes in our project - even if there's been a new release, they won't update in our project unless someone triggers it.
-   rerun all dataset generation code, including the lower level script
-   sense check the results: do they end in the expected month?
-   check the censoring dates by region are correctly entered\]

Participants with a recorded loss-to-follow-up date should be censored at loss-to-follow-up:

```{r}
# People who were lost to follow-up are censored at earliest of loss-to-follow-up and overall censoring
dat$date_cens <- pmin(dat$date_cens, dat$date_lost_followup, na.rm = TRUE)

# A few people are apparently lost to follow up in linked health records before they wore the accelerometer
# We will exclude these people - see below
```

Participants who died should be censored at death, provided this occurred before the end of records:

```{r}
# People who died are followed up to earliest of date of death and overall censoring
dat$date_fu <- dat$date_cens
dat$date_fu[dat$ind_death_record] <- pmin(dat$date_cens[dat$ind_death_record], dat$date_death[dat$ind_death_record])
```

We now record the event status at exit. We don't use 'ind_death_record' directly there may be instances of people with an event in the data after censoring (NB a minor issue in this case, more of an issue when working with hospital data so this inherits from there).

```{r}
# Mark ind_death for people with a death record during study period
dat$ind_death <- FALSE
dat$ind_death[dat$ind_death_record & (dat$date_death == dat$date_fu)] <- TRUE

# Mark ind_cv_death for participants with a CV death record in the study period
# Note we are counting any appearance of a CV code on the death register as a CVD death
# Even if this code is not the underlying (primary) cause of death
ids_death_cvd <-
  dat_death_cause$eid[grepl("I", dat_death_cause$cause_icd10)]
ind_death_cvd_record <-  dat$eid %in% ids_death_cvd
dat$ind_cv_death <- FALSE
dat$ind_cv_death[ind_death_cvd_record &
                 (dat$date_fu == dat$date_death)] <- TRUE
```

We calculate follow up time (i.e. total time on study):

```{r}
dat$fu_time <-
  as.double(difftime(dat$date_fu, dat$date_end_accel, units = "days"))
```

Alternatively, we might want to analyse the data using age as the timescale, so we add a variable for age at exit in days:

```{r}
dat$age_exit_days <- as.double(dat$age_entry_days + dat$fu_time)
dat$age_exit_days2 <-  as.double(difftime(dat$date_fu, dat$approx_dob, units = "days")) # calculation in an alternative way just so we can implement a logic check

# Logic check
if (!isTRUE(all.equal(dat$age_exit_days, dat$age_exit_days2))){
    stop("Different methods of calculating age at exit give different answers")
}
```

## Merge steps data

So far we've just been working with the non-accelerometry data. We now fold in the steps data to the broader dataset.

Merge:

```{r}
dat <- merge(dat, dat_acc, by = "eid", all.x = TRUE)
dat$med_steps <- dat$steps_daily_median_ssl.imputed
```

Chop steps into categories:

```{r}
step_cat_bounds <- c(0, 5000, 7500, 10000, 12500, 15000, 100000000000)
dat$step_cats <- cut(dat$med_steps, breaks = step_cat_bounds, right = FALSE) # Check this is correct boundarying
```

## Exclusions

We will record how many participants are excluded at each of the steps (e.g. for a flow diagram):

```{r}
tab_exc <- data.frame("Exclusion" = "Starting cohort", "Number_excluded" = NA, "Number_remaining" = nrow(dat))
```

We do the accelerometer data quality exclusions:

-   Exclude participants without step data:

```{r}
nb <- nrow(dat)
dat <- dat[!is.na(dat$med_steps), ]
tab_exc <-
  rbind(
    tab_exc,
    data.frame(
      "Exclusion" = "No step data",
      "Number_excluded" = nb - nrow(dat),
      "Number_remaining" = nrow(dat)
    )
  )
```

-   Exclude participants whose device could not be calibrated:

```{r}
nb <- nrow(dat)
dat <- dat[dat$CalibrationOK == 1, ]
tab_exc <-
  rbind(
    tab_exc,
    data.frame(
      "Exclusion" = "Poor calibration",
      "Number_excluded" = nb - nrow(dat),
      "Number_remaining" = nrow(dat)
    )
  )
```

-   Exclude participants for whom \>1% of values were clipped (fell outside the sensor's range) before or after calibration:

```{r}
nb <- nrow(dat)
dat <- dat[(dat$clips_before_cal < 0.01*dat$total_reads) & (dat$clips_after_cal < 0.01*dat$total_reads) , ]
tab_exc <-
  rbind(
    tab_exc,
    data.frame(
      "Exclusion" = "Too many clips",
      "Number_excluded" = nb - nrow(dat),
      "Number_remaining" = nrow(dat)
    )
  )
```

-   Exclude participants who had \<3 days wear or did not have wear in each hour of the 24 hour day:

```{r}
nb <- nrow(dat)
dat <- dat[dat$quality.goodWearTime == 1, ] # Note that this has already been calculated in UKB, 
# we don't need to manually calculate it: https://biobank.ndph.ox.ac.uk/showcase/field.cgi?id=90015
# But we might actually use the values from the new data processing

# 2023_01_12 - Now using quality.goodWearTime, which is calcualted from the new data processing
tab_exc <-
  rbind(
    tab_exc,
    data.frame(
      "Exclusion" = "Poor wear time",
      "Number_excluded" = nb - nrow(dat),
      "Number_remaining" = nrow(dat)
    )
  )
```

-   Exclude participants with unrealistically high overall activity values:

```{r}
nb <- nrow(dat)
dat <- dat[dat$overall_activity < 100, ] # Again can rework this with new data processing
tab_exc <-
  rbind(
    tab_exc,
    data.frame(
      "Exclusion" = "Very high overall activity",
      "Number_excluded" = nb - nrow(dat),
      "Number_remaining" = nrow(dat)
    )
  )
```

We will also exclude people who had already had a primary cardiovascular disease event in hospital data at the time they wore the accelerometer:

```{r}
nb <- nrow(dat)
dat <- dat[!(dat$ind_prev_hes_cvd), ]
tab_exc <-
  rbind(
    tab_exc,
    data.frame(
      "Exclusion" = "Prevalent cardiovascular disease in hospital data",
      "Number_excluded" = nb - nrow(dat),
      "Number_remaining" = nrow(dat)
    )
  )
```

We will also exclude people who had already had a primary cancer event in hospital data at the time they wore the accelerometer:

```{r}
nb <- nrow(dat)
dat <- dat[!(dat$ind_prev_hes_can), ]
tab_exc <-
  rbind(
    tab_exc,
    data.frame(
      "Exclusion" = "Prevalent cancer in hospital data",
      "Number_excluded" = nb - nrow(dat),
      "Number_remaining" = nrow(dat)
    )
  )
```

Missing data in adjustment variables:

```{r}
for (
  cov in c(
    "age_entry_years",
    "sex",
    "BMI",
    "ethnicity",
    "tdi_raw",
    "qualif",
    "smoking",
    "alcohol",
    "fresh_fruit",
    "processed_meat",
    "oily_fish",
    "added_salt", 
    "sr_overall_health" # needed for emmeans analyses. XXXX note no longer needed if not doing emmeans analyses
  )
){
  nb <- nrow(dat)
  print(cov)
  missing_cov <- is.na(dat[, cov])|(as.character(dat[, cov]) == "") |(as.character(dat[, cov]) == "Missing") # for safety coerce to character for second check as can return NA on some classes e.g. Date
  dat <- dat[!missing_cov,]
  tab_exc <- rbind(
    tab_exc,
    data.frame(
      "Exclusion" = paste0("Missing ", cov),
      "Number_excluded" = nb - nrow(dat),
      "Number_remaining" = nrow(dat)
    )
  )
}
```

Exclude people lost to follow up before accelerometer wear:

(See note above)

```{r}
nb <- nrow(dat)
dat <- dat[!(dat$date_cens < dat$date_end_accel), ]
tab_exc <- rbind(
  tab_exc,
  data.frame(
    "Exclusion" = "Lost to linked health record follow-up before accelerometer study entry",
    "Number_excluded" = nb - nrow(dat),
    "Number_remaining" = nrow(dat)
  )
)
tab_exc
```

## Write out

```{r}
write.csv(dat, "data/prepped_steps.csv")
```

## Clear up some of the mess ahead of running future scripts

Not strictly necessary but hopefully avoids accidentally relying on leftover data in later scripts.

```{r}
rm(list = setdiff(ls(), lsf.str())) # this setdiff is listing everything then listing only functions. So it's saying remove everything that's not a function (see https://stackoverflow.com/questions/8305754/remove-all-variables-except-functions) 
```
